Streaming CityJSON datasets

### 2024-05-01 paper/main.tex
Add storage paragraph

>>>>

Futhermore, the CityJSON specification does not prescribe the storage of CityJSONSeq, only the structure of a CityJSONSeq stream (see the five constraints above).
In practice, CityJSONSeq can be stored in a variety of ways, eg in a single file, each feature in a separate file, in a database etc., and the optimal storage solution depends on the implementing application.
